\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-29 Hierarchical-forecast-reconciliation/Figs/InsampDir_1_George.tex
Fixed graphs further

% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:34
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}\begin{document}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (288.71,191.64) {{$\large \mathfrak{s}$}};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\large \bm{R}$}};
\definecolor{drawColor}{RGB}{255,165,0}
\definecolor{fillColor}{RGB}{255,165,0}

>>>>

% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:10
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}\begin{document}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (288.71,191.64) {{$\huge \mathfrak{s}$}};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\huge \bm{R}$}};
\definecolor{drawColor}{RGB}{255,165,0}
\definecolor{fillColor}{RGB}{255,165,0}
